A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-03-19 CC/writeup.Rnw
more additions to examples

%\definecolor{Blue}{rgb}{0,0,0.5}
\definecolor{purple}{rgb}{.4,0,.8}
\newcommand{\hh}[1]{{\color{magenta} #1}}
\newcommand{\sct}[1]{{\color{purple} #1}}
\newcommand{\sctq}[1]{{\color{red} #1}} %things in red are my questions for you!

@@

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}
<<chunk_setup, echo=FALSE>>=
opts_chunk$set(tidy = TRUE, echo=FALSE, eval = FALSE, message = FALSE, fig.height = 4, fig.width = 4, fig.align = 'center')
@
<<readingdata>>=
 library(knitr)
 library(ggplot2) # needs to be the version with geom_net! 
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements, lesmis)
 load("~/Desktop/NetworksResearch/ggnet/CC/data/madmen.rda")
 email.net <- read.csv("~/Desktop/NetworksResearch/ggnet/CC/data/email-data.csv") 
 email.names <- data.frame(name = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to))))) 
@

@@

<<blood_ex, echo=TRUE>>=

@@

>>>>

%\definecolor{Blue}{rgb}{0,0,0.5}
\definecolor{purple}{rgb}{.4,0,.8}
\newcommand{\hh}[1]{{\color{magenta} #1}}
\newcommand{\sct}[1]{{\color{purple} #1}}
\newcommand{\sctq}[1]{{\color{red} #1}} %things in red are questions for you or concerns that i have.

@@

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}
<<chunk_setup, echo=FALSE>>=
opts_chunk$set(tidy = TRUE, echo=FALSE, eval = TRUE, message = FALSE, fig.height = 4, fig.width = 4, fig.align = 'center')
@
<<readingdata>>=
 library(knitr)
 library(ggplot2) # needs to be the version with geom_net! 
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements, lesmis)
 load("~/Desktop/NetworksResearch/ggnet/CC/data/madmen.rda")
 email.net <- read.csv("~/Desktop/NetworksResearch/ggnet/CC/data/email-data.csv") 
 email.names <- data.frame(name = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to))))) 
@

@@

<<blood_ex, echo=TRUE, fig.cap= "Directed network of blood type donations in humans.">>=

@@

This network is shown in figure \ref{fig:blood_ex}. 
